Exercise 3: Software Architecture in Practice Case: Beer Web Store

### 2008-03-17 trunk/SAiP/Module1/H3/doc/qualityattributes.tex
Table texts removed to preserve space.

The following scenarios (table \ref{tab:availability} and \ref{tab:performance}) is a possible outcome of prioritization and clarification of quality attribute scenarios as described above:

\begin{table}[H]
\begin{center}
\begin{tabular}{|p{0.3cm}|p{2.5cm}|p{8cm}|}
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Scenario(s):} & The customer browses the beer catalogue for descriptions and reviews and receives a timely response \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Relevant Quality Attributes:} & Availability, (Performance) \\
  \hline
  \multirow{6}{*}{\begin{sideways}{\bfseries Scenario Parts}\end{sideways}}
  & {\bfseries Source:} & The user \\
  \cline{2-3}
  & {\bfseries Stimulus:} & Browsing the beer catalogue \\
  \cline{2-3}
  & {\bfseries Artifact} & The system \\
  \cline{2-3}
  & {\bfseries Environment:} & During normal operation \\
  \cline{2-3}
  & {\bfseries Response:} & Web page presented to user \\
  \cline{2-3}
  & {\bfseries Response Measure:} & The result is presented within 5 seconds 99\% of the time, 30 seconds 0,9\% of the time and more than 30 seconds 0,1\% of the time \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Questions:} & \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Issues:} & The response measure is also dependent on the speed of the users internet connection and computer hardware. \\
  \hline
\end{tabular}
\caption{Availability scenario for the Beer Web Store}
\label{tab:availability}
\end{center}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{|p{0.3cm}|p{2.5cm}|p{8cm}|}
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Scenario(s):} & When the customer checks out, payment is validated through the payment service within 30 seconds. \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Relevant Quality Attributes:} & Performance, (Availability) \\
  \hline
  \multirow{6}{*}{\begin{sideways}{\bfseries Scenario Parts}\end{sideways}}
  & {\bfseries Source:} & The user \\
  \cline{2-3}
  & {\bfseries Stimulus:} & The customer checks out \\
  \cline{2-3}
  & {\bfseries Artifact} & The system \\
  \cline{2-3}
  & {\bfseries Environment:} & During normal operation \\
  \cline{2-3}
  & {\bfseries Response:} & Result of payment validation if presented to the user \\
  \cline{2-3}
  & {\bfseries Response Measure:} & Payment is validated through the payment service within 30 seconds \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Questions:} & \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Issues:} & The response measure is also dependent on the performance of the payment service. \\
  \hline
\end{tabular}
\caption{Performance scenario for the Beer Web Store}
\label{tab:performance}
\end{center}
\end{table}

>>>>

The following scenarios are a possible outcome of prioritization and clarification of quality attribute scenarios as described above:

\begin{table}[H]
\begin{center}
\begin{tabular}{|p{0.3cm}|p{2.5cm}|p{8cm}|}
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Scenario(s):} & The customer browses the beer catalogue for descriptions and reviews and receives a timely response \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Relevant Quality Attributes:} & Availability, (Performance) \\
  \hline
  \multirow{6}{*}{\begin{sideways}{\bfseries Scenario Parts}\end{sideways}}
  & {\bfseries Source:} & The user \\
  \cline{2-3}
  & {\bfseries Stimulus:} & Browsing the beer catalogue \\
  \cline{2-3}
  & {\bfseries Artifact} & The system \\
  \cline{2-3}
  & {\bfseries Environment:} & During normal operation \\
  \cline{2-3}
  & {\bfseries Response:} & Web page presented to user \\
  \cline{2-3}
  & {\bfseries Response Measure:} & The result is presented within 5 seconds 99\% of the time, 30 seconds 0,9\% of the time and more than 30 seconds 0,1\% of the time \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Questions:} & \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Issues:} & The response measure is also dependent on the speed of the users internet connection and computer hardware. \\
  \hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{|p{0.3cm}|p{2.5cm}|p{8cm}|}
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Scenario(s):} & When the customer checks out, payment is validated through the payment service within 30 seconds. \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Relevant Quality Attributes:} & Performance, (Availability) \\
  \hline
  \multirow{6}{*}{\begin{sideways}{\bfseries Scenario Parts}\end{sideways}}
  & {\bfseries Source:} & The user \\
  \cline{2-3}
  & {\bfseries Stimulus:} & The customer checks out \\
  \cline{2-3}
  & {\bfseries Artifact} & The system \\
  \cline{2-3}
  & {\bfseries Environment:} & During normal operation \\
  \cline{2-3}
  & {\bfseries Response:} & Result of payment validation if presented to the user \\
  \cline{2-3}
  & {\bfseries Response Measure:} & Payment is validated through the payment service within 30 seconds \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Questions:} & \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Issues:} & The response measure is also dependent on the performance of the payment service. \\
  \hline
\end{tabular}
\end{center}
\end{table}
